### 2024-01-23 iterative_monomorphisation.tex
split

\setlength{\parindent}{0pt}

@@

TODO:
   \begin{itemize}

      \item split the problems in two sets one for refining parameters and bounds, the other for overall evaluation
      \item read mangling paper in detail
      \item set up tables
      \item finish implementation (mostly there)
      \item test and evaluate implementation 
      \item (can wait) merge implementation (review code with active contributor(s) beforehand)
      \item find pretty inline setup for pseudo code
      \item (in order) write high/low level algo
      \item write implementation and evaluation
      \item write background
      \item write related work
      \item write conclusion
      \item write intro
      \item reread, spellcheck ...
    \end{itemize}

@@

@@

\begin{center}
\captionof{table}{Bounds and options to test}
\begin{tabular}{ccccc}
   \toprule
   \multicolumn{5}{c}{monomorphisation point (steps)} \\
   0 & 25 & 50 & 100 & 200 \\
   \midrule
   \multicolumn{4}{c}{new clauses multiplier} \\
   1.0 & 1.5 & 2.0 & 3.0 \\
   \midrule
   \multicolumn{3}{c}{total new clauses cap} \\
   2000 & 5000 & none\\
   \midrule
   \multicolumn{4}{c}{loop number} \\
   2 & 3 & 4 & 5 \\
   \midrule
   \multicolumn{5}{c}{monomorphisation point (steps)} \\
   0 & 25 & 50 & 100 & 200 \\

>>>>

@@

@@

Implementation in Zipperposition.

@@

We ignore the following bounds: ty var limit per clause, subst per ty var, limiting the new type args per clause
